---
title: "RMarkdown introduction"
output: html_document
---

Provides an unified authoring framework for data science, combining your code, its results, and your prose commentary. R Markdown documents are fully reproducible and support dozens of output formats, like PDFs, Word files, slideshows, and more.

In more details:

-   <https://r4ds.had.co.nz/r-markdown.html>
-   <https://bookdown.org/yihui/rmarkdown-cookbook/>

## Markdown language

Unordered list

- item 1
- item 2

Ordered list

1. first item 
2. second item

**Bold**

*italic*

***bold italic***

Mathematical expressions:

$$
\mu =  \frac{\sum x_{i}}{N} 
$$


## Code Chunks

Surround code chunks with ```` ```{r ...} ```` and ```` ``` ````. Add a chunk label and/or chunk options inside the curly braces after `r`. Use `` ` code ` `` to put inline code in the text.

```{r setup, include = FALSE}
# load libraries
library(tidyverse)
library(wooldridge)
library(stargazer)
library(viridis)
```

### Chunk Options

Options control whether a chunk is executed and how its output is displayed.

#### no options
```{r nooptions}
head(wage1)
```

#### `echo = FALSE`
```{r options echo, echo = FALSE}
head(wage1)
```

#### `eval = FALSE`
```{r options eval, eval = FALSE}
head(wage1)
```

#### `include = FALSE`
```{r options include, include = FALSE}
head(wage1)
```

----

## Introduction

This is a report on Hotel prices in Vienna in 2017. You want to understand the connection between hotel prices and guest ratings.

## Data

We use a dataset containing hotel prices and features across 46 European cities for ten different dates. The data were cleaned and filtered to include only hotels in Vienna in 2017.

```{r data import, include = FALSE}
# set working directory
setwd('/Users/martinneubrandt/Dropbox/GitHub/corvinus_econometrics')

# load dataset
hotels <- read_csv('data/hotels_vienna/hotels_vienna_main.csv')

# create factors
hotels$starrating <- factor(hotels$starrating)

```

```{r data info, echo = FALSE}
glimpse(hotels)
head(hotels)
```

## Descriptives

```{r price distribution, echo = FALSE}
# create a fancy plot about the distribution of prices
# put the mean and the median on the plot
hotels |> 
  ggplot(aes(x = price_per_night)) +
  geom_histogram(binwidth = 20,
                 aes(fill = after_stat(x)), # you have to use after_stat(x), because you need the "computed statistics" based on the x variable, not the raw x variable
                 color = 'black') +
  scale_fill_viridis() +
  geom_vline(aes(xintercept = mean(price_per_night)),
             color = 'blue',
             linetype = 'dashed',
             linewidth = 1) + # add mean
  geom_vline(aes(xintercept = median(price_per_night)),
             color = 'red',
             linetype = 'dashed',
             linewidth = 1) + # add median
  labs(title = 'Distribution of hotel prices',
       x = 'Price per night (EUR)',
       y = 'Number of hotels',
       fill = 'Price') +
  theme_classic() +
  theme(text = element_text(size = 16)) + # change the text size in the theme settings
  annotate('text',
           x = 170, y = 50,
           label = paste0('Mean: ', round(mean(hotels$price_per_night), 2)),
           color = 'blue',
           size = 5) + # add mean label
  annotate('text',
           x = 155, y = 35,
           label = paste0('Median: ', round(median(hotels$price_per_night), 2)),
           color = 'red',
           size = 5) + # add median label
  theme(legend.position = 'none') # remove legend

```

What's the connection between hotel prices and ratings?
```{r scatterplot price by ratings, echo = FALSE}
hotels |> 
  ggplot(aes(x = factor(ratings),
             y = price_per_night)) +
  geom_jitter() +
  labs(title = 'Hotel prices by rating',
       x = 'Guest rating (out of 5)',
       y = 'Price per night (EUR)',
       fill = '') +
  theme_classic() + # set the "basic" theme settings
  scale_fill_viridis(discrete = TRUE) + # set new colour filling palette
  theme(legend.position = 'none') + # remove legend
  theme(text = element_text(size = 16)) # change the text size in the theme settings

```

What's the connection between hotel prices and stars?
```{r price boxplot by stars, echo = FALSE}
hotels |> 
  ggplot(aes(x = factor(starrating),
             y = price_per_night,
             fill = factor(starrating))) +
  geom_boxplot() +
  labs(title = 'Hotel prices by stars',
       x = 'Stars',
       y = 'Price per night (EUR)',
       fill = '') +
  theme_classic() + # set the "basic" theme settings
  scale_fill_viridis(discrete = TRUE) + # set new colour filling palette
  theme(legend.position = 'none') + # remove legend
  theme(text = element_text(size = 16)) # change the text size in the theme settings

```

```{r ratings boxplot by stars, echo = FALSE}
hotels |> 
  ggplot(aes(x = factor(starrating),
             y = ratings,
             fill = factor(starrating))) +
  geom_boxplot() +
  labs(title = 'Guest ratings by stars',
       x = 'Stars',
       y = 'Guest rating (out of 5)',
       fill = '') +
  theme_classic() + # set the "basic" theme settings
  scale_fill_viridis(discrete = TRUE) + # set new colour filling palette
  theme(legend.position = 'none') + # remove legend
  theme(text = element_text(size = 16)) # change the text size in the theme settings
```

```{r distribution of distance, echo = FALSE}
# The greater the distance from the city centre, the more negative the value
# make a fancy plot about the distribution of the distance
# use the viridis color palette to fill the columns
# so the farther the column, the darker the color
hotels |> 
  ggplot(aes(x = distance)) +
  geom_histogram(bins = 30,
                 aes(fill = after_stat(x)), # you have to use after_stat(), because you need the "computed statistics based on the x variable, not the raw x variable
                 color = 'black') +
  scale_fill_viridis() +
  labs(title = 'Distribution of distance from city centre',
       x = 'Distance from city centre (miles)',
       y = 'Number of hotels',
       fill = 'Distance') +
  theme_classic() +
  theme(legend.position = 'none') + # remove legend
  theme(text = element_text(size = 16)) # change the text size in the theme settings

```

```{r all together plot, echo = FALSE}
# create a fancy plot about prices, distance, quest rating and stars
hotels |> 
  filter(distance>-10) |> 
  ggplot(aes(x = distance,
             y = price_per_night,
             shape = starrating,
             color = ratings)) +
  geom_jitter(size = 4,
              alpha = 0.75) +
  labs(title = 'Hotel prices by distance, stars, and ratings',
       x = 'Distance from city centre (miles)',
       y = 'Price per night (EUR)',
       shape = 'Stars',
       color = 'Guest rating') +
  theme_classic() + # set the "basic" theme settings
  scale_color_viridis() + # set new colour filling palette
  theme(text = element_text(size = 16)) # change the text size in the theme settings

```


## Regression

Run the following regression:

$$
ln(Price_{i}) = \beta_{0} + \beta_{1} ratings_{i} + \beta_{2} stars_{i} + \beta_{3} distance_{i} + \varepsilon_{i}
$$

```{r simple regression, echo = FALSE, message = FALSE}
# regress hotel prices on distance, stars, ratings, and offer dummy
model_base <- lm(log(price_per_night) ~ ratings,
             data = hotels)
model_stars <- lm(log(price_per_night) ~ ratings + starrating,
             data = hotels)
model_full <- lm(log(price_per_night) ~ ratings + starrating + distance,
             data = hotels)

# create regression output table using stargazer
stargazer(model_base,
          model_stars,
          model_full,
          type = 'text',
          title = 'Regression results',
          dep.var.labels = c('Log of price per night (EUR)'),
          covariate.labels = c('Guest rating (out of 5)',
                               '4 stars',
                               '5 stars',
                               'Distance (miles)'),
          no.space = TRUE,
          omit.stat = c('f', 'ser'),
          digits = 3,
          notes = c('Standard errors in parentheses')
)

```



